Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks

### 2020-03-25 paper/eccv2020submission.tex
Adding basic chart generation scripts

>>>>

This configuration results in a receptive field of $70\times70$. This means that for each $70\times70$ region of the input, the discriminator tries to guess if the region is from a real image or from a generated one.

All of the ReLUs are leaky (slope of $0.2$). Also, a final convolution is applied after the last layers that produced the a dimensional output of the discriminator. A sigmoid function is applied after the convolution.
